### 2020-08-21 sections/languages.tex
Update languages.tex

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}

\cvskill
{} 
{reading skills)} \\

@@

\cvskill
{} 
{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}

\cvskill
{} 
{{\scshape xhtml}, Notepad{\footnotesize ++}} \\

>>>>

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills),}

\cvskill
{} 
{French (elemental reading skills)} \\

@@

\cvskill
{} 
{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}

\cvskill
{} 
{{\scshape css}, {\scshape xhtml}, Notepad{\footnotesize ++}} \\
